Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-24 paper/Analisis.tex
label adentro del caption
Plots merged central and Homogeneous
2nd draft in sec 4.4 and in conclusions

\begin{figure*}
\includegraphics[width=0.45\textwidth]{Observers7t.png}
\includegraphics[width=0.45\textwidth]{Observers7tHOM.png}
\caption{Same as Figure \ref{fig:differentvelocities} but this time
  the differen lines show the line morphology for different polar angles
  $\theta$ with respect to the rotation axis. In this case each photon
  has a weight dependent on their outgoing direction. All spectra correspond
  to the same $V_{\rm max}=300$\kms, Optical   Depth $\tau=10^{7}$ and
  Central Distribution without dust.}  
  \label{fig:differentobservers}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{WidthCentral.png}
    \includegraphics[width=0.45\textwidth]{WidthHomogeneous.png}
   \caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
    \includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
    \caption{Width of the lyman-alpha line for all the models. 
  \label{figure:widthvstheta}
}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODCentral.png}
    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODHOM.png}
\caption{Position of the maxima
    in the outgoing spectra for differents Rotational velocities,
    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{NscattCentral.png}
    \includegraphics[width=0.45\textwidth]{NscattHOM.png}
\caption{Nscatt\label{fig:Nscatt}} 
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
\end{figure*}

\begin{figure*}
     \includegraphics[width=0.54\textwidth]{test3.png}%this is the homogeneous

    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{FECENTRAL.png}
  \includegraphics[width=0.45\textwidth]{FEHOMOGENEOUS.png}
   \label{figure:efvsv}\caption{Escape fraction for all the models. Left
    panels show the central distribution, while right panels show the
    homogeneous distribution} 
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
 \label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the homogeneous configuration.} 
\end{figure*}

@@

\subsection{Integrated flux in a narrow band filter}

Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position and the effect of the position of an observer. It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line. By far this is not and extensive study, it is just and ....

One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, this implies..(explain a lit of bit the method)

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline
Model & SSA22a 4980/80  & HS1700 4018/90 & HS1549 4667/80\\
\hline
V0HOM & 99965 / 98658 / & &\\
V100HOM & 99221 / 95517 / 75058 & &\\
V200HOM & 90630 / 90630 / 73938 & &\\
V300HOM & 82180 / 82180 / 71953 & &\\
V0HOMDust & 99968 / 99798 / 93132 & &\\
V100HOMDust & 99445 / 98579 / 91208 & &\\
V200HOMDust & 91439 / 90723 / 86134 & &\\
V300HOMDust & 83116 / 82630 / 79943 & &\\
\hline
\end{tabular}
\caption{
Values of fluxes for tree different NB and the our models simulated with CLARA
} 
\label{table:NBfilters}
\end{center}
\end{table}

As a first approach we may see that

@@

\section{Conclusions}
In this paper we have estimated the effects of gas bulk rotation on
the emission  of the Lyman $\alpha$ line. We based the study on the
study of a simplified configuration of an homogeneous sphere rotating
as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Lyman$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line.

>>>>

\begin{figure*}
\includegraphics[width=0.45\textwidth]{Observers7t.png}
\includegraphics[width=0.45\textwidth]{Observers7tHOM.png}
\caption{Same as Figure \ref{fig:differentvelocities} but this time
  the differen lines show the line morphology for different polar angles
  $\theta$ with respect to the rotation axis. In this case each photon
  has a weight dependent on their outgoing direction. All spectra correspond
  to the same $V_{\rm max}=300$\kms, Optical   Depth $\tau=10^{7}$ and
  Central Distribution without dust.
  \label{fig:differentobservers}}

\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{WidthvsVmax.png}
\caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
\end{figure}

\begin{figure*}%QUITARLA Y COMENTARLA
    \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
    \includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
    \caption{Width of the lyman-alpha line for all the models. 
  \label{figure:widthvstheta}
}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{maximumvsVmax.png}
\caption{Position of the maxima
    in the outgoing spectra for differents Rotational velocities,
    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
\caption{Nscatt\label{fig:Nscatt}} 
\end{figure}

\begin{figure}
    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
\end{figure}

\begin{figure}
     \includegraphics[width=0.54\textwidth]{test3.png}%this is the homogeneous

    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{EscapeFraction.png}
    \label{figure:efvsv}\caption{Escape fraction for all the models. Left panels show the central distribution, while right panels show the homogeneous distribution} 
\end{figure}

@@

\begin{figure}%QUITARLA Y COMENTARLA
  \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
 \label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the homogeneous configuration.} 
\end{figure}

@@

\subsection{Integrated flux in a narrowband filter}

Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position, also we see that shape the outgoing spectra depends in the position of an esternl observer. It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line. By far this is not and extensive study, it is just and ....

One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, for this reason we focus this analysis with the

@@

\begin{table*}
\begin{center}
\begin{tabular}{cccc}\hline
Model & SSA22a 4980/80   & HS1549 4667/80 & HS1700 4018/90\\
\hline
V0HOM & 0.997 / 0.906 / 0.405 & 0.999 / 0.965 / 0.523 & 0.999 / 0.991 / 0.662 \\
V100HOM & 0.948 / 0.819 / 0.404 & 0.981 / 0.905 / 0.511 & 0.995 / 0.962 / 0.64 \\
V200HOM & 0.748 / 0.748 / 0.403 & 0.815 / 0.815 / 0.488 & 0.879 / 0.879 / 0.59 \\
V300HOM & 0.597 / 0.597 / 0.391 & 0.661 / 0.661 / 0.457 & 0.735 / 0.735 / 0.542 \\
V0HOMDust & 0.999 / 0.997 / 0.931 & 0.999 / 0.993 / 0.863 & 0.999 / 0.998 / 0.927\\
V100HOMDust & 0.994 / 0.985 / 0.912 & 0.986 / 0.967 / 0.863 & 0.996 / 0.989 / 0.9\\
V200HOMDust & 0.914 / 0.907 / 0.861 & 0.833 / 0.815 / 0.728 & 0.889 / 0.879 / 0.81\\
V300HOMDust & 0.831 / 0.826 / 0.799 & 0.676 / 0.668 / 0.618 & 0.749 / 0.744 / 0.702\\
\hline
\end{tabular}
\caption{
Values of fluxes for tree different NB and the our models simulated with CLARA
} 
\label{table:NBfilters}
\end{center}
\end{table*}

In table \ref{table:NBfilters} we present the results of the flux in every narrowband filter for the homogenous model at different velocity and hydrogen optical depth $\tau_{0}$. As is well known an increase in the optical depth makes the line peacks separation bigger. In fact for some cases the line width is larger than the NB filer width fig.(put ref fig) for those cases we modify the redshift in order to make the peak maxima match the NB filter center. For all cases we found that as velocity increase the flux is less. \\
In the case of the dusty model we found the same trend of the flux with the velocity but in this cases the effect is no that strong. 
We also found some dependency ith the viewing angle.

@@

\section{Conclusions}
In this paper we have estimated the effects of gas bulk rotation on
the emission  of the Lyman $\alpha$ line. We based the study on the
study of a simplified configuration of an homogeneous sphere rotating
as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Lyman$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line. \\

1. Width and maxima effects

2. Avg N of scatterings

3. Integrated flux.
